A holomorphic approach to branes in twisted~$M$-theory

### 2022-09-01 fivebranes/fact.tex
weights

In this section we use the formalism of factorization algebras to give a conjectural description of observables of the universal membrane and fivebrane worldvolume theories (after twisting).
For the case at hand, our expectation for universal can be understood as the theory on a large number of membranes and fivebranes. 
We will see how this interpretation is supported by the supergravity index calculations presented in the last section.

Our ansatz for the worldvolume theories in the large $N$ limit relies on a proposal for twisted holography proposed by Costello and Li in \cite{CLsugra} and further developed by Costello, Gaiotto, Paquette in \cite{CostelloM2,CostelloOmega,costello2021twisted,CP}.
The core idea is that the algebra of operators on both sides of the duality are Koszul dual. 
Many other examples and support for this twisted holographic principle have been carried out in \cite{Oh:2021wes,Oh:2020hph,Gaiotto:2021xce}. \brian{surya add more?}

It is absolutely crucial for this proposal that we work in a derived setting using the Batalin--Vilkovisky (BV) formalism. 
The observables of any theory in the BV formalism have the structure of a factorization algebra on spacetime \cite{CG2}. 
Classically, if a theory in the BV formalism is described by a local $L_\infty$ algebra $\cL$ on spacetime $M$ then to an open set $U \subset M$ the factorization algebra of observables assigns the cochain complex
\[
\clie^\bu(\cL(U))
\]
which computes the Lie algebra cohomology of $\cL(U)$. 
The differential on this cochain complex is precisely the Chevalley--Eilenberg differential associated to the~$L_\infty$ structure maps.

At the quantum level the factorization algebra of classical observables is deformed.
Perturbatively, Costello and Gwilliam use the BV formalism to give a systematic way to study quantization within the context of factorization algebras~\cite{CG2}. 
Even in perturbation theory, the full quantum behavior of our proposal for the minimal twist of eleven-dimensional theory is an open question. 
We leave the problem to characterize the quantization to future work, and in this paper we do not address anything past tree-level in the bulk eleven-dimensional theory.

@@

We consider this decomposition at the level of the local $L_\infty$ algebra $\cG_Z$.
Recall that the Chevalley--Eilenberg cochains of this local $L_\infty$ algebra is the restricted factorization algebra~$\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\cG_Z)$. 
For each $n \in \Z$ and open set $U \subset Z$, let 
\[
\cG_Z(U)^{(n)}\subset \cG_Z(U)
\]
be the weight $n$ eigenspace with respect to this $\C^\times$ action.
As a corollary of the proposition, we get a product decomposition 
\[
\cG_Z = \prod_{n \geq -1} \cG^{(n)} .
\]
In particular, we see that $\cG^{(0)}_Z$ is itself a local Lie algebra (that we will soon describe). 
Moreover, every $\cG^{(n)}$, $n \geq -1$ is a (local) module for this local Lie algebra.

We turn to explicitly describing the first few homogenous $\C^\times$-weights of~$\cG_Z$.

@@

The first non trivial case is the weight $(-1)$ piece $\cG_Z^{(-1)}$.
We will show that
$\cG_Z^{(-1)}$ is equivalent as an abelian local Lie algebra to one of the form $\Omega^{0,\bu}(Z, \cV^{(-1)})$ where $\cV^{(-1)}$ is the holomorphic vector bundle
\[
\cV^{(-1)} = K^{1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z .
\]
The Dolbeault forms are equipped with the natural $\dbar$ operator and the $\del$ operator which takes functions to one-forms.

@@

\brian{make precise statement using $E(3|6)$.}

Particularly important for us will be the weight zero summand $\cG_Z^{(0)}$.
Again, as a local Lie algebra it is equivalent to one of the form $\Omega^{0,\bu}(Z, \cV^{(0)})$.
Since this is the weight zero component, the sheaf of sections is endowed with the structure of a Lie algebra inherited from the local $L_\infty$ algebra $\cL_{sugra}$.
When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is closely related to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
%More precisely he weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.

The holomorphic vector bundle $\cV^{(0)}$ is 
\[
\cV^{(0)} = \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
\]
The local $L_\infty$ structure of $\cL_{sugra}$ endows the Dolbeault complex of this holomorphic vector bundle with a local Lie algebra structure.
The differential turns out to be the natural $\dbar$ operator.
We describe the bracket below.

@@

The Lie bracket on $\cG_Z^{(0)}$ is induced from a Lie algebra structure on holomorphic sections of $\cV^{(0)}$ which we can describe as follows:
\begin{itemize}
\item For $\Vect^{hol}(Z)$ there is the standard commutator of holomorphic vector fields. 
This acts on the sections of $\lie{sl}(2) \otimes \cO_Z$ and $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ by Lie derivative. 
\item On sections of $\lie{sl}(2) \otimes \cO_Z$ there is the matrix commutator. 
This acts on the odd part $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ where we view $\C^2$ as the fundamental $\lie{sl}(2)$ representation. 
\item Finally, and most interestingly, there is a bracket of the form
\[
\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \times \Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \to \Vect^{hol}(Z) \oplus \lie{sl}(2) \otimes \cO_Z 
\]
given in coordinates by
\begin{multline}
[f^{ai}(z) w_a \d z_i, g^{bj} (z) w_b \d z_j] = \ep_{ijk} \ep_{ab} f^{ai} (z) g^{bj}(z) \del_{z_k} \\ + \ep_{ijk} \ep_{bc}  \del_{z_k} f^{ai}(z) g^{bj}(z) w_a \del_{w_c} + \ep_{ijk} \ep_{ac} f^{ai}(z) \del_{z_k} g^{bj}(z) w_b \del_{w_c} .
\end{multline}
The top line is a holomorphic vector field on~$Z$ and the bottom line is a $\lie{sl}(2)$-valued holomorphic function on~$Z$.
\end{itemize}

@@

\brian{mention $E(3|6)$ module structure}

\begin{prop}
Let $j \geq 1$. 
The complex of vector bundles $\cG^{(j)}$ is quasi-isomorphic to
\beqn
\Omega^{0,\bu}(Z, \cV^{(j)}) 
\eeqn
where $\cV^{(j)}$ is the super holomorphic vector bundle 
\beqn
\begin{tikzcd}
\ul{even} & \ul{odd} \\
S^{j}(\C^2) \otimes \T_Z \otimes K^{-j/2}_Z & S^{j-1}(\C^2) \otimes K^{-(j+1)/2}_Z \\
S^{j+2}(\C^2) \otimes K^{-j/2}_Z & S^{j+1}(\C^2) \otimes \T^*_Z \otimes K^{-(j+1)/2}_Z .
\end{tikzcd}
\eeqn
\end{prop}

\begin{proof}

\begin{itemize}
\item Let $f(w) \in \C[w_1,w_2]_j$ be a homogenous degree $j$ polynomial in the variables $w_1,w_2$ and suppose that $g(z) \del_{z_i}$ is a holomorphic vector field on $Z$. 
Define the $\mu$-type field
\beqn
f(w) g(z) \del_{z_i} + \cdots
\eeqn
\item Let $f(w) \in \C[w_1,w_2]_{j+2}$ be a homogenous degree $j+2$ polynomial and consider the one-form $\del f(w) = \del_{w_1} f(w)\d w_1 + \del_{w_2} f(w) \d w_2$. Using the holomorphic symplectic form we obtain the vector field
\beqn
g(z) \left(\del_{w_1} f(w) \del_{w_2} - \del_{w_2} f(w) \del_{w_1}\right) .
\eeqn
\end{itemize}
\end{proof}

@@

There are many things lacking in this definition. 
First, we do not define the $!$-dual for an arbitrary factorization algebra, only for ones of the form $\clie^\bu(\cL)$ where $\cL$ is a local Lie algebra. 
Also, we will not prove that $!$-dual satisfies any Koszul duality axioms. 
From the discussion above we see that $!$-dual does agree with Koszul duality in the case of associative algebras.\footnote{It is not difficult to see that $!$-duality for locally constant factorization algebras on $\R^n$ agrees with $\EE_n$ Koszul duality between $\clie^\bu(\fg)$, viewed as an $\EE_n$ algebra, and the $\EE_n$ enveloping algebra $U_{\EE_n} \fg$ \cite{Knudsen, Lurie,...}}

>>>>

In this section we use the formalism of factorization algebras to give a conjectural description of observables of the universal fivebrane theory after performing the holomorphic twist.
For the case at hand, our expectation for the universal theory can be understood as the worldvolume theory on a large number of fivebranes. 
We will see how this relates to the description of the states in twisted supergravity as defined in the last section.
Later, we see how our interpretation is supported by a relationship of the supergravity index to the fivebrane superconformal index.

Our ansatz for the worldvolume theories in the large $N$ limit relies on a proposal for twisted holography proposed by Costello and Li in \cite{CLsugra} and further developed by Costello, Gaiotto, Paquette in \cite{CostelloM2,CostelloOmega,costello2021twisted,CP}.
The core idea is that the algebra of operators on both sides of the duality are Koszul dual. 
Many other examples and support for this twisted holographic principle have been carried out in \cite{Oh:2021wes,Oh:2020hph,Gaiotto:2021xce}.

It is absolutely crucial for this proposal that we work in a derived setting using the Batalin--Vilkovisky (BV) formalism. 
The observables of any theory in the BV formalism have the structure of a factorization algebra on spacetime \cite{CG2}. 
Classically, if a theory in the BV formalism is described by a local $L_\infty$ algebra $\cL$ on spacetime $M$ then to an open set $U \subset M$ the factorization algebra of observables assigns the cochain complex
\[
\clie^\bu(\cL(U))
\]
which computes the Lie algebra cohomology of the $L_\infty$ algebra $\cL(U)$. 
The differential on this cochain complex is precisely the Chevalley--Eilenberg differential associated to the~$L_\infty$ structure maps.

At the quantum level the factorization algebra of observables is deformed.
Perturbatively, Costello and Gwilliam use the BV formalism to give a systematic way to study quantization within the context of factorization algebras~\cite{CG2}. 
Even in perturbation theory, the full quantum behavior of our proposal for the minimal twist of eleven-dimensional theory is an open question. 
We leave the problem to characterize the quantization to future work, and in this paper we do not address anything past tree-level in the bulk eleven-dimensional theory.

@@

We consider this decomposition at the level of the local $L_\infty$ algebra $\cG_Z$.
Recall that the Chevalley--Eilenberg cochains of this local $L_\infty$ algebra is the restricted factorization algebra~$\Bar{\pi}_* \Obs_{sugra} = \clie^\bu(\cG_Z)$. 
For each $n \in \Z$ and open set $U \subset Z$, let 
\[
\cG_Z(U)^{(n)}\subset \cG_Z(U)
\]
be the weight $n$ eigenspace with respect to this $\C^\times$ action.
As a corollary of the proposition, we get a product decomposition 
\beqn
\label{eqn:Gdecomp}
\cG_Z = \prod_{n \geq -1} \cG^{(n)} .
\eeqn
In particular, we see that $\cG^{(0)}_Z$ is itself a local Lie algebra (that we will soon describe). 
Moreover, every $\cG^{(n)}$, $n \geq -1$ is a (local) module for this local Lie algebra.

@@

The first non trivial case is the weight $(-1)$ piece $\cG_Z^{(-1)}$.
We will show that
$\cG_Z^{(-1)}$ is equivalent as an abelian local Lie algebra to one of the form $\Omega^{0,\bu}(Z, \cV^{(-1)})$ where $\cV^{(-1)}$ is the holomorphic vector bundle
\[
\cV^{(-1)} = K^{1/2}_Z \otimes \C^2 \oplus \cO_Z \oplus \Pi \T^*_Z .
\]
This Dolbeault complex is equipped with the natural $\dbar$ operator and the $\del$ operator which goes from $\Omega^{0,\bu}(Z)$ to $\Omega^{1,\bu}(Z)$.

@@

The weight zero summand $\cG_Z^{(0)}$ is special because it carries the induced structure of a local $L_\infty$ algebra on $Z$ inherited from the $L_\infty$ algebra $\cL_{sugra}$.
As a local Lie algebra it is equivalent to one of the form $\Omega^{0,\bu}(Z, \cV^{(0)})$.
We will prove the following.

\begin{prop}\label{prop:v0}
As a $\Z/2$ graded local Lie algebra on $Z$, the weight zero summand~$\cG^{(0)}_Z$ is equivalent to $\cE(3|6)$. 
\end{prop}

%Since this is the weight zero component, the sheaf of sections is endowed with the structure of a Lie algebra inherited from the local $L_\infty$ algebra $\cL_{sugra}$.
When $Z = \C^3$ we will see that the global sections of this $\Z/2$ graded $L_\infty$ algebra is closely related to the exceptional Lie algebra $E(3|6)$ studied by Kac \cite{KacClass}.
%More precisely he weight zero piece is a local Lie algebra enhancement of this exceptional Lie algebra.

To see that $\cG^{(0)}$ and $\cE(3|6)$ are equivalent as super vector bundles we must show that
\[
\cV^{(0)} \simeq \T_Z \oplus \lie{sl}(2) \otimes \cO_Z \oplus \Pi \left( \T^*_Z \otimes K^{-1/2}_Z \otimes \C^2 \right).
\]
The local $L_\infty$ structure of $\cL_{sugra}$ endows the Dolbeault complex of this holomorphic vector bundle with a local Lie algebra structure.
The differential turns out to be the natural $\dbar$ operator.
We describe the bracket below.

@@

The Lie bracket on $\cG_Z^{(0)}$ is defined from a Lie algebra structure on holomorphic sections of $\cV^{(0)}$ inherited from the $L_\infty$ algebra $\cL_{sugra}$. 
In fact, there is only a two-ary bracket, and an immediate calculation shows that it agrees with the Lie bracket on $\cE(3|6)$.

%\begin{rmk}
%In \cite{KacClass} an embedding of super Lie algebras from $E(3|6)$ into $E(5|10)$ is constructed.
%Recall that in the case $Z = \C^3$, the $\infty$-jets at $0 \in \C^3$ of the local Lie algebra $\cE(3|6)$ is precisely the exceptional super Lie algebra $E(3|6)$.
%Similarly, the $\infty$-jets at $0 \in \C^3$ of the local $L_\infty$ algebra $\cG_{\C^3}$ is $\Hat{E(5|10)}$.
%The embedding of local $L_\infty$ algebras on $Z$ from $\cE(3|6)$ into $\cG_Z$ that we just described agrees with the embedding of \cite{KacClass} upon taking $\infty$-jets.
%(Note that the central term in $\Hat{E(5|10)}$ plays no role herem since it sits in $\C^\times$-weight $-1$.)
%\end{rmk}

%\begin{itemize}
%\item For $\Vect^{hol}(Z)$ there is the standard commutator of holomorphic vector fields. 
%This acts on the sections of $\lie{sl}(2) \otimes \cO_Z$ and $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ by Lie derivative. 
%\item On sections of $\lie{sl}(2) \otimes \cO_Z$ there is the matrix commutator. 
%This acts on the odd part $\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2)$ where we view $\C^2$ as the fundamental $\lie{sl}(2)$ representation. 
%\item Finally, and most interestingly, there is a bracket of the form
%\[
%\Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \times \Pi\Omega^{1,hol}(Z, K^{-1/2}_Z \otimes \C^2) \to \Vect^{hol}(Z) \oplus \lie{sl}(2) \otimes \cO_Z 
%\]
%given in coordinates by
%\begin{multline}
%[f^{ai}(z) w_a \d z_i, g^{bj} (z) w_b \d z_j] = \ep_{ijk} \ep_{ab} f^{ai} (z) g^{bj}(z) \del_{z_k} \\ + \ep_{ijk} \ep_{bc}  \del_{z_k} f^{ai}(z) g^{bj}(z) w_a \del_{w_c} + \ep_{ijk} \ep_{ac} f^{ai}(z) \del_{z_k} g^{bj}(z) w_b \del_{w_c} .
%\end{multline}
%The top line is a holomorphic vector field on~$Z$ and the bottom line is a $\lie{sl}(2)$-valued holomorphic function on~$Z$.
%\end{itemize}

@@

We move on to give the following general description of the weight $j$ component $\cG^{(j)}$.
Since we have already described $j = -1,0$ we focus on $j \geq 1$.

\begin{prop}
Let $j \geq 1$. 
The complex of vector bundles $\cG^{(j)}$ is quasi-isomorphic to
\beqn
\Omega^{0,\bu}(Z, \cV^{(j)}) 
\eeqn
where $\cV^{(j)}$ is the super holomorphic vector bundle 
\beqn
\label{eqn:Vj}
\begin{tikzcd}
\ul{even} & \ul{odd} \\
S^{j}(\C^2) \otimes \T_Z \otimes K^{-j/2}_Z & S^{j-1}(\C^2) \otimes K^{-(j+1)/2}_Z \\
S^{j+2}(\C^2) \otimes K^{-j/2}_Z & S^{j+1}(\C^2) \otimes \T^*_Z \otimes K^{-(j+1)/2}_Z .
\end{tikzcd}
\eeqn
\end{prop}

\begin{proof}
As above, let $\C^2$ stand for the fundamental $\lie{sl}(2)$ representation and so the irreducible highest weight $j$ representation is $S^j(\C^2)$.

The weight $j \geq 1$ complex of vector bundles $\cG^{(j)}$ is readily seen to be of the following form
\beqn
\begin{tikzcd}
\ul{even} & \ul{odd} \\
\Omega^{0,\bu}(Z , \T_Z \otimes K^{-j/2}_Z) \otimes S^j(\C^2) \ar[dr, "D_1"] \\ & \Omega^{0,\bu}(Z, K^{-j/2}_Z) \otimes S^j(\C^2) \\ 
\Omega^{0,\bu}(Z , K^{-j/2}_Z) \otimes S^{j+1}(\C^2) \otimes \C^2 \ar[ur, "D_2"'] & \\
& \Omega^{1,\bu}(Z, K^{-(j+1)/2}_Z) \otimes S^{j+1}(\C^2) \\ 
\Omega^{0,\bu}(Z, K^{-(j+1)/2}_Z) \otimes S^{j+1}(\C^2) \ar[ur, "D_3"] \ar[dr, "D_4"'] \\
& \Omega^{0,\bu}(Z, K^{-(j+1)/2}_Z) \otimes S^j(\C^2) \otimes \C^2 . 
\end{tikzcd}
\eeqn

Here, as usual, the $\dbar$ operator is left implicit.
Let us describe the differentials $D_1,D_2,D_3,D_4$.
Recall that the five-fold $X = \text{Tot}(K_Z^{1/2} \otimes \C^2)$ is equipped with a non-vanishing holomorphic volume form. 
The corresponding divergence operator $\div$ restricted to the weight $j$ subspace is $\div = D_1 + D_2$. 
The differential $D_2$ is given by the identity on $\Omega^{0,\bu}(Z, K^{-j/2}_Z)$ tensored with the natural $\lie{sl}(2)$-equivariant projection
\beqn
S^{j+1}(\C^2) \otimes \C^2 \cong S^{j+2}(\C^2) \oplus S^{j}(\C^2) \twoheadrightarrow S^{j}(\C^2) .
\eeqn

The holomorphic de Rham operator on $X$ is $\del = D_3+D_4$. 
The differential $D_4$ is the identity on $\Omega^{0,\bu}(Z, K^{-(j+1)/2}$ tensored with the natural $\lie{sl}(2)$-equivariant inclusion
\beqn
S^{j+1}(\C^2) \hookrightarrow S^{j-1}(\C^2) \oplus S^{j+1}(\C^2) \cong S^j(\C^2) \otimes \C^2 .
\eeqn

There is a spectral sequence whose first term is computed by the $D_2,D_4$ cohomology. 
This term in the spectral sequence is isomorphic the complex $\Omega^{0,\bu}(Z, \cV^{(j)})$ where $\cV^{(j)}$ is as in equation \eqref{eqn:Vj}.
There are no further terms in the spectral sequence, so the result follows. 
\end{proof}

One can write down an explicit quasi-isomorphism
\beqn
\Phi \colon \Omega^{0,\bu}(Z, \cV^{(j)}) \to \cG^{(j)} 
\eeqn 
as follows.
\begin{itemize}
\item First we describe what the map looks like on the even summands.
Locally a section of $\Omega^{0,\bu}(Z, S^j(\C^2) \otimes T_Z \otimes K^{-j/2}_Z)$ is of the form
\beqn
f(w) \otimes g_i(z) \del_{z_i} 
\eeqn
where $f(w) \in \C[w_1,w_2]_j$ is a homogenous degree $j$ polynomial in the variables $w_1,w_2$ and the $g_i(z)$'s are Dolbeault forms on $Z$.
Define the divergence-free $\mu$-type field $\Phi(f(w) \otimes g_i(z) \del_{z_i})$ by the expression
\beqn
f(w) g(z) \del_{z_i} - \frac{1}{j+2} \left(\del_{z_i} g_i(z)\right) f(w) E_w
\eeqn
where $E_w = w_a \del_{w_a}$ is the Euler vector field in the direction transverse to the brane. 
\item Locally a section of $\Omega^{0,\bu}(Z, S^{j+2} \otimes K^{-j/2}_Z)$ is of the form
\beqn
f(w) \otimes g(z)  
\eeqn
where $f(w) \in \C[w_1,w_2]_{j+2}$ is a homogenous degree $j$ polynomial in the variables $w_1,w_2$ and $g(z)$ is a Dolbeault form on $Z$.
Define the divergence-free $\mu$-type field $\Phi(f(w) \otimes g(z))$ by the expression
\beqn
g(z)(\del_{w_1} f (w) \del_{w_2} - \del_{w_2} f(w) \del_{w_1}) 
\eeqn
\item Next for the odd summands.
Locally a section of $\Omega^{0,\bu}(Z, S^{j-1} \otimes K^{-(j+1)/2}_Z)$ is of the form
\beqn
f(w) \otimes g(z)  
\eeqn
where $f(w) \in \C[w_1,w_2]_{j-1}$ is a homogenous degree $j-1$ polynomial in the variables $w_1,w_2$ and $g(z)$ is a Dolbeault form on $Z$.
Define the $\gamma$-field $\Phi(f(w) \otimes g(z))$ by the expression
\beqn
\frac12 g(z)f(w)(w_1 \d w_2 - w_2 \d w_1) .
\eeqn
\item
Locally a section of $\Omega^{0,\bu}(Z, S^{j+1} \otimes T^*_Z \otimes K^{-(j+1)/2}_Z)$ is of the form
\beqn
f(w) \otimes g^i(z)  \d z_i
\eeqn
where $f(w) \in \C[w_1,w_2]_{j+1}$ is a homogenous degree $j+1$ polynomial in the variables $w_1,w_2$ and the $g^i(z)$'s are Dolbeault forms on $Z$.
Define the $\gamma$-field $\Phi(f(w) \otimes g^i(z) \d z_i)$ by the expression
\beqn
f(w) g^i (z) \d z_i .
\eeqn
\end{itemize}

The complex $\cG^{(j)}$ is manifestly a local module for the local Lie algebra $\cG^{(0)}$. 
With the identification $\cG^{(0)} \simeq \cE(3|6)$ and $\cG^{(j)} \simeq \Omega^{0,\bu}(Z, \cV^{(j)})$ we can read off this module structure completely explicitly.

Recall that as a complex of vector bundles $\cE(3|6) = \Omega^{0,\bu}(Z, \cV^{(0)}$ where 
\beqn
\cV^{(0)} 
\eeqn

\parsec[s:kacrelation]

In the case $Z = \C^3$, the product decomposition of $\cG = \cG_{\C^3}$ in equation \eqref{eqn:Gdecomp} is closely related to a decomposition of the exceptional simple super Lie algebra $E(5|10)$ studied in \cite{KR2}. 
Here, the eleven-manifold bulk is just 
\beqn
\R \times {\rm Tot}(K_{\C^3}^{1/2} \otimes \C^2) \simeq \R \times \C^5 .
\eeqn

In \S \ref{s:e510} we recalled the result from \cite{RSW} that the $\infty$-jets of $\cL_{sugra}$ at $0 \in \R \times \C^5$ is quasi-isomorphic to $\Hat{E(5|10)}$, a certain central extension of $E(5|10)$.
It follows that the $\infty$-jets of the local Lie algebra $\cG$ at $0 \in \C^3$ is also quasi-isomorphic to $\Hat{E(5|10)}$.

In \cite{KR2} the following weight decomposition of $E(5|10)$ is constructed.
Denote by $\{z_i\}$ the local coordinates along the three-fold $Z=\C^3$ that the fivebrane wraps and $\{w_a\}$ for the transverse holomorphic coordinates to the zero section in the five-fold ${\rm Tot}(K_{\C^3}^{1/2} \otimes \C^2)$.
Assign the following weights to the super Lie algebra $E(5|10)$. 
\begin{itemize} 
\item the coordinate $z_i$ has weight zero, $\wt(z_i) = 0$. 
\item the coordinate $w_a$ has weight $+1$, $\wt(w_a) = +1$. 
\item the parity of an element carries an additional weight of $-1$. 
Thus, for example, the odd element $[\d w_1 \d z_1] \in \Omega^{2,cl}(\Hat{D}^5)$ carries weight $+1 - 1 = 0$. 
(If we think about the odd part as the space of closed two-forms then equivalently this grading translates to the one-form symbol $\d(-)$ as carrying weight $-1/2$.)
\end{itemize} 
The weight grading is concentrated in degrees $\geq -1$. 
In particular, there is a decomposition of super vector spaces
\beqn\label{eqn:decomp1}
E(5|10) = \til V_{-1} \times \prod_{n \geq 0} V_n 
\eeqn
with $\til V_{-1}$ being the weight $-1$ subspace and $V_n$ being the weight $n$ subspace for $n \geq 0$.  
It is straightforward to verify that this weight grading is compatible with the super Lie algebra structure on $E(5|10)$.

At the level of $\infty$-jets the the decomposition in equation \eqref{eqn:Gdecomp} induces a weight grading of $\Hat{E(5|10)}$ which extends the one on $E(5|10)$ that we just described by declaring that the central term have weight $-1$.
In this way, we get a related decomposition of super $L_\infty$ algebras
\beqn\label{eqn:decomp2}
\Hat{E(5|10)} = \prod_{n \geq -1} V_n
\eeqn
We will refer to this as the \textit{fivebrane decomposition} of $\Hat{E(5|10)}$.
Here $V_{-1}$ is a $\C$-extension of $\til V_{-1}$ defined in the decomposition \eqref{eqn:decomp1}.
Notice that for $n \geq 0$ the $V_n$'s are the same as in the non centrally extended case.

The decomposition in equation \eqref{eqn:decomp2} has the property that $V_0$ is isomorphic to $E(3|6)$ as super Lie algebras.
In particular, for each $n$, $V_n$ is a module for $V_0 = E(3|6)$.
This is compatible with our description in proposition~\ref{prop:v0} where we showed that as local Lie algebras $\cG^{(0)} \simeq \cE(3|6)$. 
Indeed, the $\infty$-jets of the local Lie algebra $\cE(3|6)$ at $0 \in \C^3$ is quasi-isomorphic to $E(3|6)$. 
By the compatibility of our decomposition with \cite{KR2} we see that $V_n$ is quasi-isomorphic to the $\infty$-jets of $\cG^{(n)}$ at $0 \in \C^3$.

@@

There are many things lacking in this definition. 
First, we do not define the $!$-dual for an arbitrary factorization algebra, only for ones of the form $\clie^\bu(\cL)$ where $\cL$ is a local Lie algebra. 
Also, we will not prove that $!$-dual satisfies any Koszul duality axioms. 
From the discussion above we see that $!$-dual does agree with Koszul duality in the case of associative algebras.\footnote{It is not difficult to see that $!$-duality for locally constant factorization algebras on $\R^n$ agrees with $\EE_n$ Koszul duality between $\clie^\bu(\fg)$, viewed as an $\EE_n$ algebra, and the $\EE_n$ enveloping algebra $U_{\EE_n} \fg$ \cite{Knudsen, Lurie}}
